---
title: "EcoSimR"
output:
  html_document
---

**A software package to fit ecological null models**


### Overview

EcoSimR is an open source R version of the [EcoSim software project](), details about the package can be found in the [full documentation](http://docs.ecosimr.org)

### Quickstart

```{r quick install,eval=FALSE}
## Install development version
install.packages("devtools")
library(devtools)
install_github("gotellilab/EcoSimR")

```

*Co-Occurrence null model*

```{r, echo=FALSE,message=FALSE,warning=FALSE}
library(EcoSimR)
```
Data for co-occurrence null models should be a species by site matrix of incidence data.

```{r,results='asis',echo=FALSE}
knitr::kable(dataWiFinches[1:5,1:10],caption="West Indian Finch Data")
```

`EcoSimR` provides an easy way to plot and summarize output.  We'll use the *SIM9* algorithm (See table 2 Gotelli 2000) and the C-Score metric (Stone and Roberts 1990).

```{r,echo=FALSE,message=FALSE,warning=FALSE}
finchMod <- suppressMessages(cooc_null_model(dataWiFinches, algo="sim9",nReps=10000,burn_in = 500,suppressProg=T))
```


```{r eval=FALSE}
finchMod <- cooc_null_model(dataWiFinches, algo="sim9",nReps=10000,burn_in = 500)
```
```{r coocnull,fig.align='center',fig.height=5,fig.width=5}


## Summary and plot info
summary(finchMod)

plot(finchMod,type="hist")

```


See a plot of the actual matrix compared to a single simulated matrix
```{r,fig.align='center',fig.height=4,fig.width=6}

plot(finchMod,type="cooc")

```

### References
Gotelli, N.J. 2000. Null model analysis of species co-occurrence patterns. **Ecology** 81: 2606-2621  <a href = "https://www.uvm.edu/~ngotelli/manuscriptpdfs/Ecology81p2606.pdf",target = _new><i class="fa fa-file-pdf-o"></i></a>

Stone, Lewis and Roberts, Alan 1990. The checkerboard score and species distributions. **Oecologia** 85 (1): 74–79. <a href = "http://life.tau.ac.il/departments/zoology/members/stone/documents/checkerboardscoreandspecies.pdf", targe=_new><i class="fa fa-file-pdf-o"></i></a>